Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-16 cover_letter.tex
Addressed concerns regarding missing part in the algorithm

\usepackage{url}

@@

@@

>>>>

\usepackage{pseudocode}
\usepackage{url}

@@

{\tt GenerateDescription} translates the parsing tree of each nominal group
into statements. A set of rules (like the one for adjectives mentioned 
in footnote, section 5.1) help with this task.

The detailled algorithm is provided in appendix to this letter.
We would be happy to add it to the paper as well if the editor want to consider it.

{\tt Ontlogy.Find} and {\tt Ontlogy.CheckEquivalent} are simple, atomic calls to
the ontology server. The first one send a SPARQL query build from the set of 
partial statement build at the {\tt GenerateDescription} step, the second
one check for each candidate pair if {\tt candidate1 owl:sameAs candidate2}.
This check uses the classified knowledge model.

The {\tt Discrimation} algorithm is explained in details in Ros2010. The
reference has been made more explicit.

@@

\section{Appendix}

\subsection{GenerateDescription algorithms}
\label{GenerateDescription}
\begin{pseudocode}[ruled]{GenerateDescription}{group}
\label{algo|GenerateDescription}

\PROCEDURE{GenerateDescription}{group} 
   noun \GETS \CALL{GetNoun}{group} \\ 
   \IF \CALL{Ontology.Lookup}{noun} \in (Instances) \THEN
   		\BEGIN
		id \GETS \CALL{Ontology.lookup}{noun}\\	
		\RETURN {\mathcal{D} + \{ *\ {\tt sameAs}\ <id> \}}\\
		\END
   \ELSE
    	\mathcal{D} = \mathcal{D} + \{ *\ {\tt type}\ <noun>\} \\

   \\
   det \GETS \CALL{GetDeterminant}{group} \\
   \IF det \in {\mbox(possessives)} \THEN
       \mathcal{D} = \mathcal{D} + \{ *\ {\tt isRelatedTo}\ <possessor>\} \\

    \IF det \in {\mbox(demonstratives)} \THEN
        \BEGIN
        \IF \CALL{Ontology.Check}{\{<currentSpeaker>\ {\tt focusesOn}\ *\}} \THEN 
            \mathcal{D} = \mathcal{D} + \{<currentSpeaker>\ {\tt focusesOn}\ *\}
        \ELSE
            \mathcal{D} = \mathcal{D} + \CALL{AnaphoricMatching}{} \\
        \END \\
   \\
   adjs \GETS \CALL{GetAdjectives}{group} \\
   \FOREACH adj \in adjs \DO
   	\BEGIN
   		\IF adj == <other> \THEN 
   			\BEGIN
   			id \GETS \CALL{History.GetMatchingGroup}{group} \STMTNUM{8em}{st.history}\\
   			\mathcal{D} = \mathcal{D} + \{ *\ {\tt differentFrom}\ <id> \}\\
   			\RETURN{D}\\
			\END   		
   		\ELSE
	     	\mathcal{D} = \mathcal{D} + \{ *\ {\tt hasFeature}\ <adj>\} \\
    \END\\

   \\  
   nounComplements \GETS \CALL{GetNounComplements}{group} \\
   \FOREACH nouncmpl \in nounComplements \DO
     \mathcal{D} = \mathcal{D} + {\CALL{GenerateDescription}{nouncmpl}}\\

   \\  
   relativeClauses \GETS \CALL{GetSubordinateRelativeClauses}{group} \\
   \FOREACH relative \in relativeClauses \DO
   	\BEGIN
   	 \mathcal{G} \GETS \CALL{GetNominalGroups}{relative} \\
   	 \FOREACH g \in \mathcal{G} \DO
     	\mathcal{D} = \mathcal{D} + {\CALL{GenerateDescription}{g}}
    \END\\

   \\
   \RETURN{\mathcal{D}} 
\ENDPROCEDURE
\end{pseudocode}

The method called at (\ref{st.history}) consists in looking through sentences 
that have been stored in the conversation history, then extracting their nominal
group in order to retrieve the identifier of the most recently mentioned 
concept that holds the same characteristics as the nominal group that is being 
processed (algorithm~\ref{algo|History}).

\begin{pseudocode}[ruled]{History.GetMatchingGroup}{group}
\label{algo|History}
\PROCEDURE{History.GetMatchingGroup}{group}
\COMMENT{Extract Nominal group from sentences stored in the history}\\
\mathcal{H} \GETS \CALL{History.GetAllNominalGoup}{}\\
\COMMENT{Generate description of the nominal group that is being processed.} \\
\COMMENT{The adjective  "other" is to be removed before calling this routine} \\
	\mathcal{G} \GETS \CALL{GenerateDescription}{group} \\

	candidates \GETS \mathcal{H} \cap \mathcal{G}\\
	\IF \left|{candidates}\right| = 0 \THEN
    \BEGIN
      \OUTPUT{\mbox{Couldn't find another object with the same characteristics!}} \\
      \EXIT \\
    \END
   \ELSEIF \left|{candidates}\right| = 1 \THEN
      id \GETS candidates[0]
   \ELSE
   	  id \GETS \CALL{Discrimination}{candidates}\\
   \RETURN{id}
\ENDPROCEDURE
\end{pseudocode}

### 2011-07-16 paper_knowledge.tex
Addressed concerns regarding missing part in the algorithm

   \IF \left|{candidates}\right| = 0 \THEN
    \BEGIN
      \OUTPUT{\mbox{Couldn't resolve the group!}} \\
      \EXIT \\
    \END
   \ELSEIF \left|{candidates}\right| = 1 \THEN
      id \GETS candidates[0] \STMTNUM{8em}{res.easy}\\

   \ELSE
      \BEGIN
	\IF \CALL{Ontology.CheckEquivalent}{candidates} \THEN
	  id \GETS candidates[0] \\
	\ELSE
	  id \GETS \CALL{Discrimination}{candidates} \\ %\STMTNUM{0em}{st.discrimination}\\
      \END \\
   \CALL{Replace}{g, id, sentence}
\END
\end{pseudocode}
\normalsize

@@

This last example (Figure~\ref{dialog|ex3}) shows the resolution of ambiguous
concepts. In this case the user refers to ``the banana'' while two instances of 
the \concept{Banana} class exist in the ontology. The robot needs to find out 
to which instance the user is actually referring to. To this end, 
disambiguation routines~\cite{Ros2010b} find differences between the instances 
(in the example, one banana is yellow while the other one is green) and build a 
sentence through the \emph{verbalization} module to ask the user a closed 
question that will help clarify the ambiguity: ``Is it yellow or green?'' The 
user's answer is parsed and merged with the previous sentence. The resulting, 
augmented, sentence (``The green banana is good") goes again through all 
the interpretation steps. This process is repeated until no ambiguities arise. 
In the example, the \concept{banana\_02} is finally returned.

>>>>

   \IF \left|{candidates}\right| = 0 \THEN
    \BEGIN
      \OUTPUT{\mbox{Couldn't resolve the group!}} \\
      \EXIT \\
    \END
   \ELSEIF \left|{candidates}\right| = 1 \THEN
      id \GETS candidates[0]\\

   \ELSE
      \BEGIN
	\IF \CALL{Ontology.CheckEquivalent}{candidates} \THEN
	  id \GETS candidates[0] \\
	\ELSE
	  id \GETS \CALL{Discrimination}{candidates} \STMTNUM{0em}{st.discrimination}\\
      \END \\
   \CALL{Replace}{g, id, sentence}
\END
\end{pseudocode}
\normalsize

@@

This last example (Figure~\ref{dialog|ex3}) shows the resolution of ambiguous
concepts. In this case the user refers to ``the banana'' while two instances of 
the \concept{Banana} class exist in the ontology. The robot needs to find out
to which instance the user is actually referring to. To this end,
disambiguation routines (algorithm~\ref{algo|Resolution},
\emph{(\ref{st.discrimination})}, see \cite{Ros2010b} for details of the routines)
find differences between the instances (in the example, one banana is yellow
while the other one is green) and build a sentence through the
\emph{verbalization} module to ask the user a closed question that will
help clarify the ambiguity: ``Is it yellow or green?'' The user's answer is
parsed and merged with the previous sentence. The resulting, augmented,
sentence (``The green banana is good") goes again through all the
interpretation steps. This process is repeated until no ambiguities arise. 
In the example, the \concept{banana\_02} is finally returned.
